A flexible framework to prototype, develop and manage ubiquitous applications for intelligent environments

### 2013-09-20  labtempo-ubicomp-projects/UbicompMiddleware/doc/PerCom2014/percom2014_conf.tex
Started the IPGAP section and changed the SmartAndroid section

\section{SmartAndroid}
% [android and other techs]
We consolidated the concepts elaborated in the course of this project as the plafform \mbox{\textit{SmartAndroid}}\footnote{For more information visit www.tempo.uff.br/smartandroid}. The project includes the implementation of APIs framework, as well as prototyping and management interface on the Android platform.

@@

  \subsection{Interface for Management and Prototyping} \label{subsec:ipgap}
  % interface de prototipagem e gerenciamento de aplicações pervasivas
  % prototyping and management of pervasive applications interface
  % pervasive applications' management and prototyping interface
  % PAMPI
  % management and prototyping interface MPI
  [description]

>>>>

\section{SmartAndroid}
% [android and other techs]
%We consolidated the concepts elaborated in the course of this project as the platform \mbox{\textit{SmartAndroid}}\footnote{For more information visit www.tempo.uff.br/smartandroid}. The project includes the implementation of APIs to , as well as prototyping and management interface on the Android platform.

%[David]
The conceptual framework proposed at this work was tested through a reference implementation called \mbox{SmartAndroid} Project\footnote{For more information visit www.tempo.uff.br/smartandroid}. The project includes a programming API to help the developers in constructing UbiApps as well as offers basic management services to provide resource registration, discovery and localization. The SmartAndroid has been developed over Google Android platform as we believe that in a near future it will be widely used in sensors and devices embedded in furnitures and home appliances.

@@

  \subsection{Interface for Management and Prototyping} \label{subsec:ipgap}
  % interface de prototipagem e gerenciamento de aplicações pervasivas
  % prototyping and management of pervasive applications interface
  % pervasive applications' management and prototyping interface
  % PAMPI
  % management and prototyping interface MPI
  [description]\\
  %[David]
The main purpose of the [IPGAP] is provide to developers a hybrid environment where simulated and real resources can interact to each other transparently, enabling that their UbiApps are tested and evaluated through a wide variety of scenarios. RAs from sensors, actuators and household appliances can be graphically represented at our tool, along with a schematic map from the intelligent environment so that the developer can visualize the context of all resources and debug his application.
